%                            Glossary                             %

\specialhead{Glossary}

\begin{description}
\item[\textbf{ACCC}] Afghan Canadian Community Centre.
\item[\textbf{Action Script}] is an object-oriented programming language 
for creating customized web-based learning aids.  Action script 
is a language that allows the creation of web-based games and rich 
Internet applications with streaming media such as video and audio. 
\item[\textbf{ANGeL}]  Afghan Next Generation environment for Learning is an 
e-learning environment adapted from KEWL for Afghanistan.
\item[\textbf{CHI}] Computer Human Interaction.  Computer scientists 
deal with the hardware and software that drive the interface and 
thus put the computer before the human, namely, CHI.
\item[\textbf{CSV}] Comma separated variables.
\item[\textbf{ERTV}] Educational Radio and Television.
\item[\textbf{FLASH}]  is an abbreviation for Adobe, Shockwave or Macromedia 
Flash.  It is a set of multimedia technologies first introduced 
in 1996 that has become a popular method for adding animation 
and interactivity to web pages. It is also used to develop rich Internet 
applications~\cite{allaire02}.
\item[\textbf{HCI}] Human Computer Interaction. It is the physical and mental 
boundary between users and input/output devices of a computer. All 
interactive computer processes require that a human gives some instruction 
to the computer, e.g. to store data, and receives feedback from the computer.
\item[\textbf{Informant Design}] is a framework used to involve various participants 
in the design process. ``It allows making maximal use of the input 
of the participants at different stages of the design''~\cite{scaife97}.
%(Michael Scaife 1997). 
\item[\textbf{KEWL}] Knowledge Environment for Web-based Learning.  An e-learning 
management system developed at the University of the Western Cape, 
South Africa.
\item[\textbf{Participatory Design}]  Is an approach that respects users as 
partners in the design process and ``in doing so explicitly gives them 
a more equal and responsible role''~\cite{scaife97}.
%(Michael Scaife 1997).
% \item[\textbf{UWC}]  The University of the Western Cape.
\item[\textbf{UNESCO}] United Nations Educational, Scientific and Cultural Organization.
\item[\textbf{UNICEF}] The United Nations Children's Fund.
\item[\textbf{USAID}] United States Agency for International Development.

\end{description}

